Project-I by Group Sao Paulo

### 2015-11-02 report/paper.tex

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/y_histogram.png}
	\caption{Histogram of $y$. We can see three bursts of data.}
	\label{fig:reg_yHistogram}
\end{figure}

@@

\begin{figure}[!h] % !t
\center
\subfigure[$y$ in function of $55^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim6.png} \label{fig:reg_dim6}}
\hfill
\subfigure[$y$ in function of $6^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim55.png} \label{fig:reg_dim55}}
\caption{Graphs of $y$ in function of the input dimensions most correlated with the output.}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/clusters_train.png}
	\caption{Clusters obtained along the two most correlated dimensions. We can see three clearly delimited groups of data.}
	\label{fig:reg_clustersTrain}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\subfigure[First k-means applied along the most correlated dimension of $X$ with $y$.]{\includegraphics[width=2.6in]{figures/clusters_phase1.png} \label{fig:reg_clustersTest1}}
	\hfill
	\subfigure[Second k-means applied along the second most correlated dimension of $X$ with $y$.]{\includegraphics[width=2.6in]{figures/clusters_phase2.png} \label{fig:reg_clustersTest2}}
	\caption{Steps of k-means clustering for test-data.}
	\label{fig:reg_clustersTest}
\end{figure}

@@

Figure ~\ref{fig:reg_alphaRMSE} shows the train and test RMSE for a step size $\alpha$ varied from $10^{-3}$ to $10^{-0.5}$ with $20$ points in between. The convergence condition was reached when the variation of $\beta$ between two iterations was lower than $1.5 \alpha$. Cross-validation was made using $66 \% $ of the data as train data and the rest as test data.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=4in]{figures/lambdaRMSE.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_alphaRMSE}
\end{figure}

Figure ~\ref{fig:reg_lambdaRMSE} shows the train and test RMSE for $\lambda$ varied from $10^{-3}$ to $10^{7}$ with $60$ points in between. Cross-validation was made using $66 \% $ of the data as train data and the rest as test data. We can see that $\lambda$ should be chosen between $0$ and $100$ to have the best prediction and that $\lambda$ higher than $1000$ increases the RMSE and the model under-fits.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=4in]{figures/lambdaRMSE.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_lambdaRMSE}
\end{figure}

Figure TODO compares the three regression methods with $\alpha = TODO$ for the gradient descent and $\lambda = TODO$ for ridge regression. We see that TODO.

@@

\section{Summary}
In this report, we ...

>>>>

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.2in]{figures/y_histogram.png}
	\caption{Histogram of $y$. We can see three bursts of data.}
	\label{fig:reg_yHistogram}
\end{figure}

@@

\begin{figure}[!h] % !t
\center
\subfigure[$y$ in function of $55^{th}$ dimension of $X$.]{\includegraphics[width=2.2in]{figures/dim6.png} \label{fig:reg_dim6}}
\hfill
\subfigure[$y$ in function of $6^{th}$ dimension of $X$.]{\includegraphics[width=2.2in]{figures/dim55.png} \label{fig:reg_dim55}}
\caption{Graphs of $y$ in function of the input dimensions most correlated with the output.}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.2in]{figures/clusters_train.png}
	\caption{Clusters obtained along the two most correlated dimensions. We can see three clearly delimited groups of data.}
	\label{fig:reg_clustersTrain}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\subfigure[First k-means applied along the most correlated dimension of $X$ with $y$.]{\includegraphics[width=2.2in]{figures/clusters_phase1.png} \label{fig:reg_clustersTest1}}
	\hfill
	\subfigure[Second k-means applied along the second most correlated dimension of $X$ with $y$.]{\includegraphics[width=2.2in]{figures/clusters_phase2.png} \label{fig:reg_clustersTest2}}
	\caption{Steps of k-means clustering for test-data.}
	\label{fig:reg_clustersTest}
\end{figure}

@@

Figure ~\ref{fig:reg_alphaRMSE} shows the train and test RMSE for a step size $\alpha$ varied from $10^{-3}$ to $10^{-0.5}$ with $20$ points in between. The convergence condition was reached when the variation of $\beta$ between two iterations was lower than $1.5 \alpha$. Cross-validation was made using $66 \% $ of the data as train data and the rest as test data. We observe that the bias is higher and the variance globally lower for small values of $\alpha$. The RMSE is optimal for $\alpha \approx 0.2$. With higher $\alpha$ values, gradient descent is not able to converge and the error goes to $\infty$.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/alphaRMSEBox.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_alphaRMSE}
\end{figure}

Figure ~\ref{fig:reg_lambdaRMSE} shows the train and test RMSE for $\lambda$ varied from $10^{-3}$ to $10^{7}$ with $60$ points in between. Cross-validation was made using $66 \% $ of the data as train data and the rest as test data. We can see that $\lambda$ should be chosen between $0$ and $100$ to have the best prediction and that $\lambda$ higher than $1000$ increases the RMSE and the model under-fits. For high $\lambda$ values, the model and estimation bias are increased as their variance is reduced.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/lambdaRMSE.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_lambdaRMSE}
\end{figure}

Figure ~\ref{fig:reg_compareMethods} compares three regression methods with $\alpha = 0.25$ for the gradient descent and $\lambda = 100$ for ridge regression. We see that TODO.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=4in]{figures/lambdaRMSE.png}
	\caption{Boxplots of train and test RMSE for least-squares, least-square with gradient descent and ridge regression.}
	\label{fig:reg_compareMethods}
\end{figure}

@@

\section{Summary}
In this report, we analyse a regression and a classification dataset. We used k-means clustering and PCA to preprocess the regression data. We found that TODO.
We separated the classification data using a binary dimension that classify the data in two different distributions along the variable of the input data.We found that TODO.
